%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------

%---------------------------------------------------------
\cvsubsection{Work}
\begin{cventries}
  \cventry
    {Software Engineer Intern} % Job title
    {Opt Incubate Inc.} % Organization
    {Tokyo, Japan} % Location
    {Dec. 2017 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Construct CI/CD server using CentOS on AWS, Gitlab and Jenkins.}        
        \item {Implemented a part of web application, backend API in Python, their interface in PHP, and frontend Google Map service.}
        \item {Fabricated and maintain corporate web site include server.}
      \end{cvitems}
    }

  \cventry
    {Web Media Writer Intern} % Job title
    {Opt Incubate Inc.} % Organization
    {Tokyo, Japan} % Location
    {Dec. 2016 - Nov. 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Wrote articles on the owned media to get much access and to lead to service.}
        \item {Assembled business raw data onto Microsoft PowerPoint graphs or tables.}
      \end{cvitems}
    }
\end{cventries}    

%---------------------------------------------------------
\cvsubsection{Teaching}
\begin{cventries}
  \cventry
    {Teaching Assistant} % Job title
    {School of Social Informatics, Aoyama Gakuin University} % Organization
    {Kanagawa, Japan} % Location
    {Apr. 2017 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Support beginning programming students in computer laboratories.}
        \item {Grade homework for Network Server Constructions.}
      \end{cvitems}
    }
\end{cventries}

%---------------------------------------------------------
\cvsubsection{Leadership}
\begin{cventries}
  \cventry
    {Co-founder \& Representative director} % Job title
    {Norden Wind Ensemble} % Organization
    {Kanagawa, Japan} % Location
    {Jan. 2018 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Founded a wind ensemble organization consists of highschool graduates}
        \item {Organize whole activities such as music selection, getting practice space and planning concert.}
      \end{cvitems}
    }
\end{cventries}

%---------------------------------------------------------
